\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage[margin=0.5in]{geometry}
\setlength{\textheight}{700pt}
\usepackage{url}

\usepackage{tikz}
% \usepackage{color} % Redundant: xcolor is already loaded and is more powerful

% hyperref should be loaded last for best compatibility
\usepackage[colorlinks=true,urlcolor=purple]{hyperref}

\frenchspacing
\pagestyle{empty}

\usepackage{titlesec}
% This command formats the unnumbered sections (\section*) to be uppercase with a rule underneath.
\titleformat{\section*}{\Large\usefont{OT1}{phv}{b}{n}}{}{0pt}{\MakeUppercase}[\vspace{-2pt}\titlerule[0.4pt]\vspace{4pt}]

\newcommand{\sepspace}{\vspace*{1em}}

% Corrected command for the name: uses #1 instead of \#1 and robust centering.
\newcommand{\MyName}[1]{{\Huge\usefont{OT1}{phv}{b}{n}\centering #1\par}\normalsize\normalfont}

% Corrected command for new sections: uses #1 instead of \#1.
\newcommand{\NewPart}[1]{\section*{\MakeUppercase{#1}}}

\begin{document}

\MyName{Bheki Ngwenya}
\begin{center}
\large
Johannesburg South Africa $\cdot$ 0797394470 $\cdot$ \href{mailto:ngwenyabheki276@gmail.com}{ngwenyabheki276@gmail.com} \\
\href{https://linkedin.com/in/bheki-ntando-ngwenya01}{linkedin.com/in/bheki-ntando-ngwenya01} $\cdot$ \href{https://github.com/Mabhekane0100000}{github.com/Mabhekane0100000}
\end{center}

\sepspace

\NewPart{Summary}
A versatile professional with a unique, hybrid background in both network engineering and full-stack software development. Leveraging a modern tech stack including Java, Node.js, React, and Docker, I excel at designing, building, and deploying robust applications with a deep understanding of the underlying network infrastructure. This dual expertise, demonstrated at CMC Networks, allows for the creation of highly optimized and resilient systems from the ground up. I am driven to apply this comprehensive skill set to solve complex technical challenges and deliver high-performance solutions.

\sepspace

\NewPart{Skills}
java $\cdot$ c\# $\cdot$ nodejs $\cdot$ reactjs $\cdot$ mongodb $\cdot$ docker $\cdot$ typescript $\cdot$ javascript $\cdot$ c++ $\cdot$ system analysis

\sepspace

\NewPart{Experience}
\noindent\textbf{Network Engineer \& Software Developer} \hfill 2023-07-01 - Present \\
\textit{CMC Networks} \hfill \textit{Building H, The Woodlands, Office Park, 20 Woodlands Dr, Woodmead, Sandton, 2191}
\begin{itemize}[leftmargin=*, label={-}]
    \item Engineered and maintained real-time monitoring systems achieving 99.9\% uptime across critical infrastructure using Python and monitoring tools.
    \item Developed automated reporting dashboards reducing manual report generation time by 60\% through data integration and visualization.
    \item Collaborated with cross-functional teams to implement security policies and anomaly detection systems, strengthening network perimeter defense.
    \item Led incident response and root cause analysis for critical system failures, documenting solutions and implementing preventive measures.
    \item Built centralized Data Lake architecture streamlining performance metrics collection and analysis across multiple systems.
    \item Integrated multiple service platforms (Fresh Services, PRTG, inventory systems) enabling real-time asset visibility and management.
\end{itemize}

\sepspace

\NewPart{Education}
\noindent\textbf{BSc in Computer Science} \hfill 2020 \\
\textit{North-West University}

\end{document}