\documentclass[paper=a4,fontsize=11pt]{scrartcl} 
							
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     
\usepackage{graphicx}                    
\usepackage[svgnames]{xcolor}           
\usepackage[margin=0.5in]{geometry}
\setlength{\textheight}{700pt}
\usepackage{url}

\usepackage{tikz}
\usepackage{kpfonts} 
\usepackage{color}
\usepackage{amssymb}
\newcommand*\Hs{\ensuremath{\color{red}\varheartsuit}}

%%% Heart-stab command
\newcommand{\heartstab}{%
\begin{tikzpicture}[baseline=(current bounding box.center)]%
\draw [line width=0.0mm, white] (3.5ex,0.4ex) -- (3.5ex,0.4ex);
\node at (0,0) {\Large{$\Hs$}};
\draw [line width=0.30mm, black] (-0.7ex,0.7ex) -- (1.2ex,1.2ex);%
\draw [line width=0.50mm, black] (0.8ex,0.65ex) -- (0.55ex,1.45ex);%
\end{tikzpicture}%
}

%%% Squiggly arrow
\newcommand{\squigarr}{%
{\Large \color{blue}$\rightsquigarrow$}%
}

\usepackage[colorlinks=true,urlcolor=purple]{hyperref}

\frenchspacing              
\pagestyle{empty}           

\usepackage{sectsty}

\sectionfont{%			            
	\usefont{OT1}{phv}{b}{n}%		% bch-b-n: CharterBT-Bold font
	\sectionrule{0pt}{0pt}{-5pt}{3pt}}

\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{0.5em}}		% Vertical space macro

\newcommand{\MyName}[1]{ % Name
		\Huge \usefont{OT1}{phv}{b}{n} \hfill #1
		\par \normalsize \normalfont}
		
\newcommand{\MySlogan}[1]{ % Slogan (optional)
		\large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
		\par \normalsize \normalfont}
		
\newcommand{\NameEmailPhoneSiteGithub}[5]{
        \Huge \usefont{OT1}{phv}{m}{n} \textbf{#1} 
        \large \usefont{OT1}{phv}{m}{n} \hfill #2\hspace{25pt}#3
        
        \textit{Anti Curriculum Vitae}\hfill \textit{website } #4 \hspace{25pt}\textit{github } #5 
        \par \normalsize \normalfont
}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
		\noindent\hangindent=2em\hangafter=0 % Indentation
		\parbox{\spacebox}{        % Box to align text
		\textit{#1}}			   % Entry name (birth, address, etc.)
		\hspace{1.5em} #2 \par}    % Entry value	

%%% Begin Document
%%% ------------------------------------------------------------
\begin{document}

\NameEmailPhoneSiteGithub{Bheki Ngwenya}{ngwenyabheki275 gmail.com}{27797394470}{https:  bankhosa.com}{https:  github.com Mabhekane}
\sepspace
\NewPart{Professional Summary}
Dynamic Network Engineer and Full-stack Software Developer adept at bridging complex infrastructure with cutting-edge application layers. Expertly leverages Java, C  , Node.js, React.js, and MongoDB to architect robust, scalable solutions and consistently optimize system performance within intricate network environments. Committed to continuous learning and delivering innovative software products that drive technical excellence.
\sepspace
\NewPart{Work Experience}
\textbf{Network Engineer    Software Developer} \hfill 07 2022 - 07 2025
\textit{} \hfill Building H, The Woodlands, Office Park, 20 Woodlands Dr, Woodmead, Sandton, 2191
\begin{itemize}
\item Engineered and optimized real-time monitoring systems with Python, achieving 99.9   uptime across critical network infrastructure.
\item Developed and deployed automated reporting dashboards, reducing manual generation time by 60   through robust data integration and visualization.
\item Strengthened network perimeter defense by implementing advanced security policies and anomaly detection systems.
\item Reduced critical system failures by spearheading incident response and implementing proactive preventive measures based on Root Cause Analysis.
\end{itemize}
\sepspace
\NewPart{Education}
\textbf{BSc} \hfill 07 2025
\textit{North-West University} \hfill Potchestroom,  North-West University
GPA: 65
\sepspace
\NewPart{Skills}
\SkillsEntry{technical}{java, c  , nodejs, reactjs, monodb, git, typescript, javasript}
\sepspace
\NewPart{Certifications}
\textbf{AWS Certified Solutions Architect} \hfill 05 2024
\textit{Amazon}
\textit{Expires: 05 2027}
\sepspace
\NewPart{Languages}
\textbf{English} \hfill conversational
\textbf{Siswati} \hfill native
\sepspace
\NewPart{References}
References available upon request.
\sepspace

\end{document}