\documentclass[paper=a4,fontsize=11pt]{scrartcl} 
							
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     
\usepackage{graphicx}                    
\usepackage[svgnames]{xcolor}           
\usepackage[margin=0.5in]{geometry}
\setlength{\textheight}{700pt}
\usepackage{url}

\usepackage{tikz}
\usepackage{kpfonts} 
\usepackage{color}
\usepackage{amssymb}
\newcommand*\Hs{\ensuremath{\color{red}\varheartsuit}}

%%% Heart-stab command
\newcommand{\heartstab}{%
\begin{tikzpicture}[baseline=(current bounding box.center)]%
\draw [line width=0.0mm, white] (3.5ex,0.4ex) -- (3.5ex,0.4ex);
\node at (0,0) {\Large{$\Hs$}};
\draw [line width=0.30mm, black] (-0.7ex,0.7ex) -- (1.2ex,1.2ex);%
\draw [line width=0.50mm, black] (0.8ex,0.65ex) -- (0.55ex,1.45ex);%
\end{tikzpicture}%
}

%%% Squiggly arrow
\newcommand{\squigarr}{%
{\Large \color{blue}$\rightsquigarrow$}%
}

\usepackage[colorlinks=true,urlcolor=purple]{hyperref}

\frenchspacing              
\pagestyle{empty}           

\usepackage{sectsty}

\sectionfont{%			            
	\usefont{OT1}{phv}{b}{n}%		% bch-b-n: CharterBT-Bold font
	\sectionrule{0pt}{0pt}{-5pt}{3pt}}

\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{0.5em}}		% Vertical space macro

\newcommand{\MyName}[1]{ % Name
		\Huge \usefont{OT1}{phv}{b}{n} \hfill #1
		\par \normalsize \normalfont}
		
\newcommand{\MySlogan}[1]{ % Slogan (optional)
		\large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
		\par \normalsize \normalfont}
		
\newcommand{\NameEmailPhoneSiteGithub}[5]{
        \Huge \usefont{OT1}{phv}{m}{n} \textbf{#1} 
        \large \usefont{OT1}{phv}{m}{n} \hfill #2\hspace{25pt}#3
        
        \textit{Anti Curriculum Vitae}\hfill \textit{website } #4 \hspace{25pt}\textit{github } #5 
        \par \normalsize \normalfont
}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
		\noindent\hangindent=2em\hangafter=0 % Indentation
		\parbox{\spacebox}{        % Box to align text
		\textit{#1}}			   % Entry name (birth, address, etc.)
		\hspace{1.5em} #2 \par}    % Entry value	

%%% Begin Document
%%% ------------------------------------------------------------
\begin{document}

\NameEmailPhoneSiteGithub{Bheki Ngwenya}{ngwenyabheki275 gmail.com}{27797394470}{https:  bankhosa.com}{https:  github.com Mabhekane}
\sepspace
\NewPart{Professional Summary}
Results-driven Network Engineer and Full-Stack Software Developer with expertise in seamlessly integrating infrastructure and application layers to architect high-performance, scalable solutions. Proficient in leveraging Java, C  , Node.js, React.js, and MongoDB, with a proven track record of developing robust systems that significantly enhance operational efficiency. Committed to optimizing complex network environments and delivering innovative software products that exceed performance objectives.
\sepspace
\NewPart{Work Experience}
\textbf{Network Engineer    Software Developer} \hfill 07 2022 - 07 2025
\textit{} \hfill Building H, The Woodlands, Office Park, 20 Woodlands Dr, Woodmead, Sandton, 2191
\begin{itemize}
\item Achieved and sustained 99.9   uptime across critical infrastructure by designing and optimizing real-time monitoring systems.
\item Reduced manual report generation time by 60   through the successful development and deployment of automated data integration and visualization dashboards.
\item Strengthened overall network security posture by implementing advanced anomaly detection systems, leading to a demonstrable reduction in potential vulnerabilities.
\item Minimized critical system downtime and recurrence by effectively leading incident response and implementing proactive long-term preventative solutions.
\end{itemize}
\sepspace
\NewPart{Education}
\textbf{BSc} \hfill 07 2025
\textit{North-West University} \hfill Potchestroom,  North-West University
GPA: 65
\sepspace
\NewPart{Skills}
\SkillsEntry{technical}{java, c  , nodejs, reactjs, monodb, git, typescript, javasript}
\sepspace
\NewPart{Certifications}
\textbf{AWS Certified Solutions Architect} \hfill 05 2024
\textit{Amazon}
\textit{Expires: 05 2027}
\sepspace
\NewPart{Languages}
\textbf{English} \hfill conversational
\textbf{Siswati} \hfill native
\sepspace
\NewPart{References}
References available upon request.
\sepspace

\end{document}